04_DESeq_sexes

### 2019-07-18 analysis/04_DESeq2_sexes.Rmd
now with bar plots

library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)
library(viridis)

@@

myDEGs <- plot_grid(a,
          #d + theme_siggenes,
          #b + theme_noaxislabels,
          #e + theme_noaxislabels,
          c ,
          #f + theme_noaxislabels,
          nrow = 1) 
myDEGs

@@

@@

```{r candidates, eval =T}
plotcandidates(dds.female_hypothalamus, colData.female_hypothalamus, "female hypothalamus")
plotcandidates(dds.female_pituitary, colData.female_pituitary,  "female pituitary")
plotcandidates(dds.female_gonad, colData.female_gonad,  "female gonad")
plotcandidates(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus")
plotcandidates(dds.male_pituitary,  colData.male_pituitary, "male pituitary")
plotcandidates(dds.male_gondad, colData.male_hypothalamus , "male gonad")
```

>>>>

library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)
library(viridis)
library(forcats)

@@

myDEGs <- plot_grid(a + theme_noaxislabels,
          d + theme_siggenes,
          b + theme_noaxislabels,
          e + theme_noaxislabels,
          c + theme_noaxislabels,
          f + theme_noaxislabels,
          nrow = 3) 
myDEGs

@@

## Plot only a subset of DEGs that relate to hypotheses

```{r totalDEGbarsplots}
g <- plotserialDEGs(DEGs.female_hypothalamus, "Female hypothalamus")
h <- plotserialDEGs(DEGs.female_pituitary, "Female pituitary")
i <- plotserialDEGs(DEGs.female_gonad, "Female gonad")
j <- plotserialDEGs(DEGs.male_hypothalamus, "Male hypothalamus")
k <- plotserialDEGs(DEGs.male_pituitary, "Male pituitary")
l <- plotserialDEGs(DEGs.male_gondad, "Male gonad")

mybarplots <- plot_grid(g, h , i , j ,k , l, nrow = 2) 
mybarplots

pdf("../figures/sexes/totalDEGbarsplots-1.pdf", width = 10, height = 6)
plot(mybarplots)
dev.off()
```

@@

```{r candidates, eval =F}
plotcandidates(dds.female_hypothalamus, colData.female_hypothalamus, "female hypothalamus")
plotcandidates(dds.female_pituitary, colData.female_pituitary,  "female pituitary")
plotcandidates(dds.female_gonad, colData.female_gonad,  "female gonad")
plotcandidates(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus")
plotcandidates(dds.male_pituitary,  colData.male_pituitary, "male pituitary")
plotcandidates(dds.male_gondad, colData.male_hypothalamus , "male gonad")
```
